Forecasting the Support of Kamala Harris in 2024 U.S. Presidential Election using a Model-Based Approach

### 2024-11-04 paper/ForecastingtheSupportofKamalaHarrisin2024U.S.PresidentialElection.qmd
update paper

Where: $W$ is the weight parameters calculated from the product of
**sample size weight** and recency **weight**.

@@

-   **Recency Weight**: Applied through an exponential decay function,
    exp(-recency \* 0.1), where "recency" represents the days since the
    poll was conducted. This ensures that more recent data carries more
    weight, while older polls have reduced influence.

@@

For each candidate, we isolate polls specifically for Kamala Harris and
Donald Trump, retaining only high-quality polls with a numeric_grade of
2 or higher—given that the average numeric_grade is approximately 2.175,
with a median of 1.9. We also handle placeholder values in state
information by setting entries marked as NA to National, and creating a
national_poll indicator, assigning a value of 1 for value in state equal to National and 0 for others. Dates are standardized using the lubridate
package to facilitate accurate time-based analysis.

>>>>

Where: $W$ is the weight parameters calculated from the product of
**sample size weight** and **recency weight**.

@@

-   **Recency Weight**: Applied through an exponential decay function,
    exp(-recency \* 0.1), where "recency" represents the days since the
    poll was conducted, and 0.1 is the decay rate of the poll. This ensures that more recent data carries more
    weight, while older polls have reduced influence.

@@

For each candidate, we isolate polls specifically for Kamala Harris and
Donald Trump, retaining only high-quality polls with a numeric_grade of
2 or higher—given that the average numeric_grade is approximately 2.175,
with a median of 1.9. We also handle placeholder values in state
information by setting entries marked as NA to National, and creating a
national_poll indicator, assigning a value of 1 for value in state equal to National and 0 for others. We also filter the population with only likely voters and registered voters. Dates are standardized using the lubridate
package to facilitate accurate time-based analysis.
